Locally Conservative Discontinuous Petrov-Galerkin Finite Elements for Fluid Problems

### 2013-11-19 docs/Truman/LocalConservation/paper/paper.tex
adding robustness paragraph by jesse

Let $\bs U_h:=U_h\times\bs S_h\times\hat U_h\times\hat F_h\subset L^2(\Omega_h)\times\bs
L^2(\Omega_h)\times H^{\frac{1}{2}}(\Gamma_h)\times H^{-\frac{1}{2}}(\Gamma_h)$
be a finite-dimensional subspace, and let $\bs u_h:=(u_h.\bfsigma_h,\hat
u_h\hat t_h)\in\bs U_h$ be a group variable. The element conservative DPG scheme is
derived from the Lagrangian:
\begin{equation}
L(\bs u_h,\lambda_k)=\frac{1}{2}\norm{R_V^{-1}(b(\bs
u_h,\cdot)-(f,\cdot))}^2_{\bs V}-\sum_K\lambda_K(b(\bs u_h,(1_K,\bs0))-l((1_K,\bs0)))\,,
\label{eq:lagrangian}
\end{equation}
where $(1_K,\bs0)$ is the test function in which $v=1$ on element $K$ and 0 elsewhere and $\btau=\bs0$ everywhere.

>>>>

% jesse robustness section

We note that, for convection-diffusion problems, we are particularly interested in designing a \textit{robust} DPG method.  Specifically, we are interested in designing methods whose behavior does not change as the diffusion parameter $\epsilon$ becomes very small.  Naive Galerkin methods for convection-diffusion tend to suffer from a lack of robustness; specifically, the finite element error is bounded by a constant factor of the best approximation error, but the constant is often proportional to $\epsilon^{-1}$.  Our aim is to design a DPG method with this in mind.  We follow the methodology introduced by Heuer and Demkowicz in \cite{DemkowiczHeuer}: the ultra-weak variational formulation for convection-diffusion can be refactored as
\[
b\LRp{\LRp{u,\sigma,\uh,\fnh},\LRp{\tau,v}} = \sum_{K\in \Oh}\LRs{\LRa{\fnh,v}_{\delta K} + \LRa{\uh,\tau_n}_{\delta K} + \LRp{u,\div \tau - \beta\cdot\grad v}_{L^2(K)} + \LRp{\sigma,\frac{1}{\epsilon} \tau + \grad v}_{L^2(K)}},
\]
modulo application of boundary data.  If we choose specific \textit{conforming} test functions satisfying the adjoint equations
\begin{align*}
\div \tau - \beta \cdot \grad v &= u,\\
\frac{1}{\epsilon} \tau + \grad v &= \sigma,
\end{align*}
then evaluating $b\LRp{\LRp{u,\sigma,\uh,\fnh},\LRp{\tau,v}}$ at these specific test functions returns back $\norm{u}^2 + \norm{\sigma}^2$, the $L^2$ norm of our field variables.  Multiplying and dividing through by the test norm $\norm{v}_V$, we have
\[
\norm{u}_{\L}^2 + \norm{\sigma}_{\L}^2 = b\LRp{\LRp{u,\sigma,\uh,\fnh},\LRp{\tau,v}} = \frac{b\LRp{\LRp{u,\sigma,\uh,\fnh},\LRp{\tau,v}}}{\norm{v}_V}\norm{v}_V \leq \norm{u,\sigma,\uh,\fnh}_E\norm{v}_V,
\]
where 
\[
\norm{u,\sigma,\uh,\fnh}_E = \sup_{v\in V\setminus\LRc{0}}\frac{b\LRp{\LRp{u,\sigma,\uh,\fnh},\LRp{\tau,v}}}{\norm{v}_V}
\]
is the DPG energy norm.  If we can robustly bound the test norm $\norm{v}_V \lesssim \LRp{\norm{u}_{\L}^2+\norm{\sigma}^2_{\L}}^{1/2}$ (i.e. derive a bound from above with a constant independent of $\epsilon$), then we can divide through to get
\[
\LRp{\norm{u}_{\L}^2 + \norm{\sigma}_{\L}^2}^{\frac{1}{2}} \lesssim \norm{u,\sigma,\uh,\fnh}_E.
\]
In other words, the energy norm in which DPG is optimal bounds independently of $\epsilon$ the $L^2$ norm; as we drive our energy error down to zero, we can expect that the $L^2$ error will also decrease regardless of $\epsilon$.

We note that the construction of the test norm $\norm{v}_V$ for a robust DPG method depends on two things: the test norm, as well as the adjoint equation.  In \cite{DemkowiczHeuer}, the standard problem with Dirichlet conditions enforced over the entire boundary was considered; in \cite{ChanHeuerThanhDemkowicz2012}, boundary conditions were chosen for the forward problem such that the induced adjoint problem was regularized and contained no strong boundary layers, allowing for the construction of a stronger test norm on $V$.  We adopt a slight modification of the test norm introduced in \cite{ChanHeuerThanhDemkowicz2012} for numerical experiments here, which is motivated and explained in more detail in Section~\secref{sec:confusionPlate}.

Having reviewed and laid the foundation for DPG methods, we can now formulate our conservative DPG scheme.  % added by Jesse
Let $\bs U_h:=U_h\times\bs S_h\times\hat U_h\times\hat F_h\subset L^2(\Omega_h)\times\bs
L^2(\Omega_h)\times H^{\frac{1}{2}}(\Gamma_h)\times H^{-\frac{1}{2}}(\Gamma_h)$
be a finite-dimensional subspace, and let $\bs u_h:=(u_h.\bfsigma_h,\hat
u_h\hat t_h)\in\bs U_h$ be a group variable. The element conservative DPG scheme is
derived from the Lagrangian:
\begin{equation}
L(\bs u_h,\lambda_k)=\frac{1}{2}\norm{R_V^{-1}(b(\bs
u_h,\cdot)-(f,\cdot))}^2_{\bs V}-\sum_K\lambda_K(b(\bs u_h,(1_K,\bs0))-l((1_K,\bs0)))\,,
\label{eq:lagrangian}
\end{equation}
where $(1_K,\bs0)$ is the test function in which $v=1$ on element $K$ and 0 elsewhere and $\btau=\bs0$ everywhere.
